A Horrocks-type theorem for even orthogonal $K_2$

### 2019-08-23 dl-paper.tex
Fixed small bugs

Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ is a larger subgroup of $\St(\rD_\ell, R)$ than $\K_2(\rD_\ell, R)$.
More precisely, from~\cite[157]{Ba74} and Snake lemma it follows that \[\KO_2(2n, R)/\K_2(\rD_n, R) \cong \Ker(\mathrm{Spin}(2n, R) \to \mathrm{SO}(2n, R)) = \mu_2(R).\]
On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which
$G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
%Notice that $\K_2(\rD_n, R) \subset \mathrm{KO}_2(n, R)$.

>>>>

Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_\ell, R)$, but the converse is not true. On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
